Cache is King: Presenting a Suite of Fast, Correlation Function Codes

### 2015-03-25 paper/ms.tex
Fixed Makefile and silenced clang static analyzer

Modern cpu's have a hierarchy of memory locations; the smallest and fastest are closest to the cores while the largest and slowest are the
farthest. All cpu instructions need to be carried out from cpu registers - there are $\sim 10-30$ registers typically available and the 
access times can be thought of as instantaneous. Next up is the $L1$ cache divided into $L1D$ for data and $L1I$ for instructions cache. Since 
the cpu always necessarily executes instructions that are close together, we will ignore the instruction cache from now on. Typical $L1$ cache 
sizes range from 64KB to 128 KB. Next level up is the $L2$ cache, typically $\sim$ 256KB to 1 MB. The last level cache or the $L3$ cache 
is usually shared across all cores on the socket and can be 10 MB to 40 MB.

>>>>

Modern cpu's have a hierarchy of memory locations; the smallest (and fastest) are closest to the cores while the largest (and slowest) are the
farthest. All cpu instructions need to be carried out from cpu registers - there are $\sim 10-30$ registers typically available and the 
access times can be thought of as instantaneous. Next up is the $L1$ cache divided into $L1D$ for data and $L1I$ for instructions cache. Since 
the cpu always necessarily executes instructions that are close together, we will ignore the instruction cache from now on. Typical $L1$ cache 
sizes range from 64KB to 128 KB. Next level up is the $L2$ cache, typically $\sim$ 256KB to 1 MB. The last level cache or the $L3$ cache 
is usually shared across all cores on the socket and can be 10 MB to 40 MB.
